Responses to the Reviewers' Comments

### 2024-11-02 Response/Paper_Res.tex
Rev_V7.8

Second, to highlight the impacts of the LSTM network and dueling architecture, we have extended the performance evaluation by comparing the performance of our proposed algorithm with vanilla DQN and DDQN \cite{van2016deep}. We have added Fig. 7 to Section VI of the revised manuscript.
This figure highlights the positive effect of workload prediction by the LSTM network. This prediction contributes to improving the efficient utilization of the processing resources of ENs, leading to faster convergence of the QECO algorithm and achieving a higher average QoE compared to other methods.

@@

Furthermore, to enhance the evaluation of our work, we have extended the performance analysis by comparing QECO with vanilla DQN and DDQN \cite{van2016deep}. This comparison illustrates the impacts of the LSTM network and dueling architecture. We have added Fig. 7 to Section VI of the revised manuscript.

@@

\begin{my}{0.5cm}{0.5cm}	
\rev{\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{QECO Algorithm (Training Process)}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{\textcolor{blue}{Input:}}} \renewcommand{\algorithmicensure}{\textbf{\textcolor{blue}{Output:}}} \Require \textcolor{blue}{experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ from MD $i \in \mathcal{I}$} \Ensure \textcolor{blue}{parameter vector $\theta_i^{\text{E}}$} 
	\end{algorithmic} 
\end{algorithm} 
\end{minipage}
\vspace{5mm}

\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{QECO Algorithm (Offloading Decision)}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{Input:}} \renewcommand{\algorithmicensure}{\textbf{Output:}}\Require state space $\mathcal{S}$, action space $\mathcal{A}$
			\Ensure MD $i \in \mathcal{I}$ experience  \textcolor{blue}{ $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$}
		\end{algorithmic} 
	\end{algorithm} 
\end{minipage}}
\end{my}

>>>>

Second, to highlight the impacts of the LSTM network and dueling architecture, we have extended the performance evaluation by comparing the performance of our proposed algorithm with two baseline schemes, vanilla DQN and DDQN \cite{van2016deep}. We have added Fig. 7 to Section VI of the revised manuscript.
This figure highlights the positive effect of workload prediction by the LSTM network. This prediction contributes to improving the efficient utilization of the processing resources of ENs, leading to faster convergence of the QECO algorithm and achieving a higher average QoE compared to other methods.

@@

Furthermore, to enhance the evaluation of our work, we have extended the performance analysis by comparing QECO with two baseline schemes, vanilla DQN and DDQN \cite{van2016deep}. This comparison illustrates the impacts of the LSTM network and dueling architecture. We have added Fig. 7 to Section VI of the revised manuscript.

@@

\begin{my}{0.5cm}{0.5cm}	
\rev{\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{Offloading Decision Algorithm at MD $i \in \mathcal{I}$}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{\textcolor{blue}{Input:}}} \renewcommand{\algorithmicensure}{\textbf{\textcolor{blue}{Output:}}} \Require \textcolor{blue}{experience $(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t), \boldsymbol{q}_i(t), \boldsymbol{s}_i(t+1))$ from MD $i \in \mathcal{I}$} \Ensure \textcolor{blue}{parameter vector $\theta_i^{\text{E}}$} 
	\end{algorithmic} 
\end{algorithm} 
\end{minipage}
\vspace{5mm}

\begin{minipage}[b]{0.87\textwidth} 
	\begin{algorithm}[H] \caption{Training Process Algorithm at EN $j \in \mathcal{J}$}\label{alg:cap2} \centering 
		\begin{algorithmic}[1] \renewcommand{\algorithmicrequire}{\textbf{Input:}} \renewcommand{\algorithmicensure}{\textbf{Output:}}\Require state space $\mathcal{S}$, action space $\mathcal{A}$
			\Ensure MD $i \in \mathcal{I}$ experience  \textcolor{blue}{ $(\hspace{-0.2mm}\boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{a}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{q}_i(\hspace{-0.2mm}t\hspace{-0.2mm}), \boldsymbol{s}_i(\hspace{-0.2mm}t\hspace{-0.3mm}+\hspace{-0.3mm}\hspace{-0.2mm}1\hspace{-0.2mm}\hspace{-0.2mm})\hspace{-0.2mm})$}
		\end{algorithmic} 
	\end{algorithm} 
\end{minipage}}
\end{my}
